Three $\approx$40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-29 papers/ms.tex
update ms

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new and
  refined view of how stellar clusters evolve.
  Here we present an analysis of a group of $\approx$40 million
  year old stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.
  The group includes four known Kepler Objects of Interest:
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$),
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), and
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$).
  Kepler-1627 is a Neptune-sized planet in a sub-component of the
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.
  Here we focus on the latter three systems, which are in other
  sub-components of the complex (RSG-5 and CH-2).
  Based on kinematic evidence from Gaia, stellar rotation periods from
  TESS, and spectroscopy, these three systems are also $\approx$40
  million years old.
  More specifically, we find that Kepler-1643 (in RSG-5) is
  $46^{+9}_{-7}$\,Myr old, while KOI-7368 and KOI-7913 (in CH-2) are
  $36^+{10}_{-8}$\,Myr old.
  Based on the transit shapes and high resolution imaging, they are
  all most likely planets, with false positive probabilities of
  $6\times10^{-9}$, $5\times10^{-3}$, and $1\times10^{-4}$ for
  Kepler-1643, KOI-7368, and KOI-7913 respectively.
  Kepler-1643 and KOI-7913 are therefore the first empirical
  demonstration that mini-Neptunes with sizes of $\approx$2 Earth
  radii exist at ages of $\approx$40 million years.
\end{abstract}

@@

The discovery of a young planet requires two claims to be fulfilled:
the planet must exist, and its age must be secured.  Spaced-based
photometry from K2 and TESS has yielded a number of young planets for
which the planetary evidence comes from transits, and the age evidence
is based on either cluster membership \citep[{\it
e.g.},]{Mann_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,nardiello_pathosII_2020}
or else on correlates of youth such as stellar rotation, photospheric
lithium abundances, x-ray activity, or emission line strength
\citep[{\it e.g.},]{zhou_2021_tois,hedges_toi-2076_2021}.

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar group memberships
\citep[{\it e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.
Broadly speaking these analyses cluster on the stellar positions and
on-sky velocities measured by Gaia, with varying degrees of filtering
and supervision.  One important result is the identification of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  These
spatially diffuse groups typically have velocity dispersions of
$\approx$1\kms, though they can be much higher due to both projection
effects and internal dynamics.  As an extreme example, in the Hyades
the apparent velocities of stars in the tidal tails are expected to
span up to $\pm 40$\kms relative to the cluster center
\citep{jerabkova_800_2021}.  The stars in such diffuse regions can be
verified to be the same age as the core members ({\it i.e.}, coeval)
through analyses of color-absolute magnitude diagrams, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are many
implications for our understanding of star formation and cluster
evolution \citep[{\it e.g.},][]{dinnbier_tidal_2020}, a more immediate
consequence is that we now know the ages of many more stars, including
previously known planet hosts.

@@

Many of the relevant stellar parameters can be gleaned by inspecting
Figure~\ref{fig:age}.  The known planet-hosting stars in Cep-Her span
spectral types of G8V (Kepler-1627) to K8V (KOI-7913 A).  The
secondary in the KOI-7913 system is only marginally cooler than the
primary (SpType $\approx$M0V).
The latter system is 3$\farcs$501 
%FIXME FIXME FIXME TODO TODO TODO
A Solar-mass star with solar metallicity arrives at the zero-age main
sequence at $t\approx40$ million years (CITE CHOI MESA), and so these
stars are in the end stages of their pre-main-sequence contraction.
Their Gaia EDR3 parallaxes span X.X to Y.Y, corresponding to distances
between X.X and Y.Y parsecs.

To derive the spectroscopic parameters $(T_{\rm eff}, \log g_\star,
[{\rm Fe/H}])$ and  the equivalent width of the Li\,\textsc{I}
from the 6708\,\AA\ doublet, we acquired spectra.  Specifically, we
acquired iodine-free HIRES spectra for Kepler-1643 (YYYY/MM/DD) and
KOI-7913 (YYYY/MM/DD and YYYY/MM/DD), where for the latter the two
different epochs corresponded to observations of the secondary and
primary respectively.  The acquisition and analysis followed the
standard reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  For KOI-7368, we acquired TRES spectra on
YYYY/MM/DD and YYYY/MM/DD.  CITE METHOD PAPER.
The results are given in Table~\ref{tab:sysparams}.

Table~\ref{tab:sysparams} summarizes
%
%from the 
%
%
%\citep[{\it e.g.},][]{soderblom_ages_2014}, we acquired an iodine-free
%spectrum from Keck/HIRES on the night of 2021 March 26 using the
%standard setup and reduction techniques of the California Planet
%Survey \citep{howard_cps_2010}.  Following the equivalent width
%measurement procedure described by \citet{bouma_2021_ngc2516}, we find
%${\rm EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   This value does not
%correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Nonetheless,
%given the stellar effective temperature (Table~\ref{tab:starparams}),
%this measurement is in agreement with expectations for a
%$\approx40$\,Myr star ({\it e.g.}, as measured in IC~2602 by
%\citealt{randich_gaiaeso_2018}).  It is also larger than any lithium
%equivalent widths measured by \citet{berger_identifying_2018} in their
%analysis of 1{,}301 Kepler-star spectra.
%
%
%% rotation period from plot_rotation_period_windowslider.py
%Based on the spatial and kinematic association of \sn\ with the \cn,
%and the assumption that the planet formed shortly after the star, it
%seems likely that \sn\ is the same age as the cluster. There are two
%consistency checks on whether this is true: rotation and lithium.
%Based on the Kepler light curve, the rotation period is
%$2.642\pm0.042$\,days, where the quoted uncertainty is based on the
%scatter in rotation periods measured from each individual Kepler
%quarter.  This is consistent with comparable cluster members
%(Figure~\ref{fig:age}).

%\subsection{Kepler\,1627A}
\subsection{Kepler\,1643}
\subsection{KOI-7368}
\subsection{KOI-7913}
Is a binary.

>>>>

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new and
  refined view of how stellar clusters evolve.
  Here we present an analysis of a group of $\approx$40 million
  year old stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.
  The group includes four known Kepler Objects of Interest:
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$),
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), and
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$).
  Kepler-1627 is a Neptune-sized planet in a sub-component of the
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.
  Here we focus on the latter three systems, which are in other
  sub-components of the complex (RSG-5 and CH-2).
  Based on kinematic evidence from Gaia, stellar rotation periods from
  TESS, and spectroscopy, these three systems are also $\approx$40
  million years old.
  More specifically, we find that Kepler-1643 (in RSG-5) is
  $46^{+9}_{-7}$\,Myr old, while KOI-7368 and KOI-7913 (in CH-2) are
  $36^{+10}_{-8}$\,Myr old.
  Based on the transit shapes and high resolution imaging, they are
  all most likely planets, with false positive probabilities of
  $6\times10^{-9}$, $5\times10^{-3}$, and $1\times10^{-4}$ for
  Kepler-1643, KOI-7368, and KOI-7913 respectively.
  These planets are therefore the first empirical
  demonstration that mini-Neptunes with sizes of $\approx$2 Earth
  radii exist at ages of $\approx$40 million years.
\end{abstract}

@@

The discovery of a young planet requires two claims to be fulfilled:
the planet must exist, and its age must be secured.  Spaced-based
photometry from K2 and TESS has yielded a number of young planets for
which the planetary evidence comes from transits, and the age evidence
is based on either cluster membership \citep{Mann_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,nardiello_pathosII_2020}
or else on correlates of youth such as stellar rotation, photospheric
lithium abundances, x-ray activity, or emission line strength
\citep{zhou_2021_tois,hedges_toi-2076_2021}.

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar group memberships
\citep[{\it e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.
Broadly speaking these analyses cluster on the stellar positions and
on-sky velocities measured by Gaia, with varying degrees of filtering
and supervision.  One important result is the identification of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  These
spatially diffuse groups typically have velocity dispersions of
$\approx$1\kms, though they can be much higher due to both projection
effects and internal dynamics.  As an extreme example, in the Hyades
the velocities of stars in the tidal tails are expected to
span up to $\pm 40$\kms relative to the cluster center
\citep{jerabkova_800_2021}.  The stars in such diffuse regions can be
verified to be the same age as the core members ({\it i.e.}, coeval)
through analyses of color-absolute magnitude diagrams, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are many
implications for our understanding of star formation and cluster
evolution \citep{dinnbier_tidal_2020}, a more immediate
consequence is that we now know the ages of many more stars, including
previously known planet hosts.

@@

Some of the most salient stellar parameters of the KOIs in Cep-Her can
be gleaned by inspecting Figure~\ref{fig:age}.  They span spectral
types of G8V (Kepler-1627) to K8V (KOI-7913 A).  The secondary in the
KOI-7913 system is marginally cooler than the primary.  Since a
Solar-mass star with solar metallicity arrives at the zero-age main
sequence at $t\approx40$ million years \citep{choi_mesa_2016}, these
stars are all in the late stages of their pre-main-sequence
contraction.  Their heliocentric distances are $\approx$260\,pc
(KOI-7913 and KOI-7368, in CH-2) and $\approx$340\,pc (Kepler-1643, in
RSG-5).

To derive spectroscopic parameters $(T_{\rm eff}, \log g_\star, [{\rm
Fe/H}])$ and to analyze spectroscopic youth proxies such as the
Li\,\textsc{I} 6708\,\AA\ doublet equivalent width and H$\alpha$
emission, we acquired spectra.  The system-by-system details follow.
The results are summarized in Table~\ref{tab:sysparams}.

%\citep[{\it e.g.},][]{soderblom_ages_2014}, we acquired an iodine-free
%spectrum from Keck/HIRES on the night of 2021 March 26 using the
%standard setup and reduction techniques of the California Planet
%Survey \citep{howard_cps_2010}.  Following the equivalent width
%measurement procedure described by \citet{bouma_2021_ngc2516}, we find
%${\rm EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   This value does not
%correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Nonetheless,
%given the stellar effective temperature (Table~\ref{tab:starparams}),
%this measurement is in agreement with expectations for a
%$\approx40$\,Myr star ({\it e.g.}, as measured in IC~2602 by
%\citealt{randich_gaiaeso_2018}).  It is also larger than any lithium
%equivalent widths measured by \citet{berger_identifying_2018} in their
%analysis of 1{,}301 Kepler-star spectra.
%
%
%% rotation period from plot_rotation_period_windowslider.py
%Based on the spatial and kinematic association of \sn\ with the \cn,
%and the assumption that the planet formed shortly after the star, it
%seems likely that \sn\ is the same age as the cluster. There are two
%consistency checks on whether this is true: rotation and lithium.
%Based on the Kepler light curve, the rotation period is
%$2.642\pm0.042$\,days, where the quoted uncertainty is based on the
%scatter in rotation periods measured from each individual Kepler
%quarter.  This is consistent with comparable cluster members
%(Figure~\ref{fig:age}).

%\subsection{Kepler\,1627A}

\subsection{Kepler\,1643}

For Kepler-1643,
we acquired an iodine-free spectrum from Keck/HIRES
...
%FIMXE TODO TODO TODO WORDS LET'S GO!

spectra  (YYYY/MM/DD) and KOI-7913 (YYYY/MM/DD and
YYYY/MM/DD), where for the latter the two different epochs
corresponded to observations of the secondary and primary
respectively.  The acquisition and analysis followed the standard
reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  For KOI-7368, we acquired TRES spectra on
YYYY/MM/DD and YYYY/MM/DD.  CITE METHOD PAPER.

\subsection{KOI-7368}
\subsection{KOI-7913}
Is a binary.
The latter system is 3$\farcs$501 
%FIXME FIXME FIXME TODO TODO TODO
